---
title: "STAT 345 Lab Seven"
author: "James Bartsch"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Git and GitHub

1. Follow the instructions in the notes on installing/setting up Git and 


```{r}
usethis::use_git_config(user.name = "James-Bartsch", user.email = "jamesbartsch1399@uwlax.edu")
usethis::create_github_token() 
credentials::set_github_pat("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")

```



2. Create a simple R file (script, .rmd, etc.) and add some code to it (any code will do!).
```{r}
file(description = "code directly from the built in '?file' help page", open = "", blocking = TRUE, #code directly from the built in '?file' help page 
     encoding = getOption("encoding"), raw = FALSE,
     method = getOption("url.method", "default"))

```


3. Commit your file, then Push it to GitHub. Visit your GitHub repository online to verify that your code pushed correctly.


4. Edit your code. You can change the code or add new lines. Commit and push again.
5. Submit the link to your repository on Canvas.
6. Have a great break!

